Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-13 paper-webserver.tex
ADD: fishers images into tex

\section{DISCUSSION}
% Gist, we address the the "Limitations" of \cite{de2015trends}.
% Namely:
% 1. Custom formats.
% 2. Use of legacy tech (SQL) means youu can't accomadate "Big-Data" goals.

>>>>

On comparison tasks, Spfy can retrieve and compare 1 million nodes or attributes in the graph database in aproximately 70 seconds \ref{fig:fishers_performance}. Performance scales linearly with the number of genomes involved in the comparison, or the number of target nodes retrieved per genome.

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_genomes.png}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_targets.png}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{images/fishers_overall.png}
\endminipage
\caption{Runtimes of Fisher's Exact Test depending on the number of nodes/attributes involved in the comparison. Left: Runtimes as the number of genomes involved increases for a fixed (107) number of targets per genome. Center: Runtimes as the number of targets involved increased for a fixed (116) number of genomes per target. Right: Runtimes as the total number of targets retrieved increases; the total number of targets is calculated as follows: (Number Genomes Group A + Number Genomes Group B) x Number Targets per Genome. In all cases, we see a linear increase in runtime as the number of targets or the number of genomes involved increases.}\label{fig:fishers_performance}
\end{figure}

\section{DISCUSSION}
% Gist, we address the the "Limitations" of \cite{de2015trends}.
% Namely:
% 1. Custom formats.
% 2. Use of legacy tech (SQL) means youu can't accomadate "Big-Data" goals.{}
